Optimal forward modeling of gravitational fields using tesseroids with adaptive discretization

### 2014-09-10 body.tex
Added table with shell data

The computation point can be considered at any longitude and latitude because of
the symmetry of the spherical shell.

Fig.~\ref{fig:sample}b shows that the largest errors are concentrated directly
on top of the tesseroid.

Making the comparison between the tesseroid

We perform the computations on an $11 \times 11$ point regular grid.

@@

\begin{table}
    \caption{Parameters of the spherical shell.}
    \label{tab:shell}
    \begin{tabular}{lr}
        $\rho$                    & $2.67\ g.cm^{-3}$ \\
        $\Delta r$                & $1\ km$ \\
        $r_1 = R$                 & $6,378.137\ km$ \\
        $r_2 = r_1 + \Delta r$    & $6,379.137\ km$ \\
    \end{tabular}
\end{table}

>>>>

Fig.~\ref{fig:sample}b shows that the largest errors are concentrated directly
on top of the tesseroid and near the quadrature nodes.

Because of that, comparing the shell and tesseroid effects at a single point
would not be representative of the actual error committed.

The gravitational fields of the spherical shell are the same for any point at a
radial distance $r>r_2$ because of the symmetry of the shell.

We perform the computations for the tesseroid model on an $11 \times 11$ point regular grid.

@@

\begin{table}
    \caption{Parameters of the spherical shell.}
    \label{tab:shell}
    \begin{tabular}{ll}
        $\rho$                    & $2.67\ g.cm^{-3}$ \\
        $\Delta r$                & $1\ km$\\
        $r_1 = R$                 & $6,378.137\ km$ \\
        $r_2 = r_1 + \Delta r$    & $6,379.137\ km$ \\
    \end{tabular}
\end{table}

\begin{table}
    \caption{Reference values of the gravitational potential, attraction, and
    gravity gradient tensor of the spherical shell.}
    \label{tab:shell-data}
    \begin{tabular}{ll}
        $V$                    &    $14278.021191\ m^2.s^{-2}$ \\
        $g_z$                  &    $223.788630$ mGal \\
        $g_{xx} = g_{yy}$      &    $-0.350758$ E\"otv\"os\\
        $g_{zz}$               &    $0.701517$ E\"otv\"os\\
    \end{tabular}
\end{table}
